---
title: "Overview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FALL254753rury0000)
```

# Overview

This package provides various functions used in Math 4753: Applied Statistical Methods. Below are some examples.

## mycltb

This function creates randdom samples from a binomial distribution, takes the mean, and builds a histogram. The dotted line shows the theoretical curve. The function models the central limit theorem.

```{r}
mycltb(n=20,iter=10000)
```

## myboot2

This function uses the bootstrap method to generate a density for a desired statistic based on a sample. The function returns a barplot with point and interval estimates.

```{r}
sam <- rnorm(30)
myboot2(x = sam)
```

## ntickets

This function calculates the optimum number of tickets to sell on a plane for given number of seats, probability of a seat being filled, and the acceptable risk level. The function returns the normal approximation and discrete estimates for the number of tickets.

```{r}
ntickets()
```

## myncurve

The function returns a normal curve with the cumulative probability shaded.

```{r}
myncurve(mu = 0,sigma = 1,a = 1)
```
